---
title: "BigQuery & GDS 2022 Prez- Georgia Voter File"
author: "Jasmin Fernandez Castillo"
date: "`r Sys.Date()`"
output: slidy_presentation
---

## Intro
- Name: Jasmin [pronounced ("Hazz-Mean")]
- Pronouns: THEY/THEM/THEIRS

- to view the hyperlinks, make sure you press "Ctrl" and then click. Else they wont open. The CTRL (i think its command for Apple) will open the hyperlinks in a new tab. 

- the big query hyperlink might not work if you are not logged into a google account

[Google Data Studio Dashboard](https://datastudio.google.com/reporting/0ff24aff-bee8-427f-b02e-b45c7856ca4b)

[GitHub Project](https://github.com/jf2987/Big_Query_Project-)

[Executive Report](https://docs.google.com/document/d/1WXB-zkv5wC3GcfnpDY_AYyB5i6NZ5InH_5wgcFi-QGk/edit?usp=sharing)

[BigQ_EDA Code](https://console.cloud.google.com/bigquery?sq=1056050731331:ed47d7b8df624810bed63ba5dcece4fc)

## The TS GA Sub setted Data

```{r tabsets, echo=FALSE}
setwd("C:/Users/cogps/Downloads")

data_2<-read.csv("GA_Data_Updates_2.csv")

head(data_2)

```

## R Markdown

-Subsetting at with the TS Smart variable was considered best for it resulted in a bigger sample than voter file state variable

- The TS Smart Model State scores had 
```{r , echo=FALSE}
##TS_SMART
nrow(data_2[data_2$vb_tsmart_state == "GA", ])
# 15709 with ts smart
```
rows

-Whereas the Voter file State scores had
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_state == "GA", ])
# 13863 with voter file 

```
rows

## Model Scores 
- Comparable to the Real Data at the State level
```{r , echo=FALSE}
data_2$State_match<-ifelse(data_2$vb_tsmart_state==data_2$vb_vf_reg_state,"Match","No_Match")
library(sur)
percent.table(data_2$State_match, y = NULL)

barplot(percent.table(data_2$State_match, y = NULL))

```

## Coordinate Exploration

```{r , echo=FALSE}
library(tidyverse)
library(sf)
library(mapview)
mapview(data_2, xcol = "vb_reg_longitude", ycol = "vb_reg_latitude", crs = 4269, grid = FALSE)


```

## MARIETTA & MACON

-This is the numbers of folks in MARIETTA:
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_city == "MARIETTA", ])

```
-This is the numbers of folks in MACON:
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_city == "MACON", ])

```

## Now we can Look at age Break Down of Macon & Marietta


```{r , echo=FALSE}
GA_data_S<-subset(data_2, vb_tsmart_city == "MACON" | vb_tsmart_city == "MARIETTA")

library(ggplot2)
bp<-ggplot(data=GA_data_S, aes(x=vb_tsmart_city, y=vb_voterbase_age)) +
         geom_boxplot()
bp+coord_cartesian(ylim=c(0, 112))+ scale_y_continuous(breaks=seq(0, 112, 10)) 


```

## ## Now we can Look at Sex Break Down of Macon & Marietta

This is the Sex breakdown of Macon:
```{r , echo=FALSE}
library(tidyverse)
Macon <- data_2  %>% 
  filter(vb_tsmart_city == "MACON")
library(sur)
percent.table(as.factor(Macon$vb_voterbase_gender))
```

This is the Sex breakdown of Marietta:
```{r , echo=FALSE}
Marietta <- data_2  %>% 
  filter(vb_tsmart_city == "MARIETTA")

library(sur)
percent.table(as.factor(Marietta$vb_voterbase_gender))

```



## There was a difference in the breakdown of Race

Racial Breakdown of Macon:

```{r , echo=FALSE}
percent.table(as.factor(Macon$vb_voterbase_race))
```
Racial Breakdown of Marietta:

```{r , echo=FALSE}
percent.table(as.factor(Marietta$vb_voterbase_race))
```


## Ending Statements

-If I had more time:

- I would look further into the partisan scores and available scores

- I would also provide better visualizations and better code

- and additional analyses with open source datasets