---
title: "BigQuery & GDS 2022 Prez- Georgia Voter File"
author: "Jasmin Fernandez Castillo"
date: "`r Sys.Date()`"
output: slidy_presentation
---

## Intro
- Name: Jasmin [pronounced ("Hazz-Mean")]
- Pronouns: THEY/THEM/THEIRS

## The TS GA Sub setted Data

```{r tabsets, echo=FALSE}
setwd("C:/Users/cogps/Downloads")

data_2<-read.csv("GA_Data_Updates_2.csv")

head(data_2)

```

## R Markdown

-Subsetting at with the TS Smart variable was considered best for it resulted in a bigger sample than voter file state variable

- The TS Smart Model State scores had 
```{r , echo=FALSE}
##TS_SMART
nrow(data_2[data_2$vb_tsmart_state == "GA", ])
# 15709 with ts smart
```
rows

-Whereas the Voter file State scores had
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_state == "GA", ])
# 13863 with voter file 

```
rows

## Model Scores 
- Comparable to the Real Data at the State level
```{r , echo=FALSE}
data_2$State_match<-ifelse(data_2$vb_tsmart_state==data_2$vb_vf_reg_state,"Match","No_Match")
library(sur)
percent.table(data_2$State_match, y = NULL)

barplot(percent.table(data_2$State_match, y = NULL))

```

## Coordinate Exploration

```{r , echo=FALSE}
library(tidyverse)
library(sf)
library(mapview)
mapview(data_2, xcol = "vb_reg_longitude", ycol = "vb_reg_latitude", crs = 4269, grid = FALSE)


```

## MACON

-This is the numbers of folks in MARIETTA:
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_city == "MARIETTA", ])

```
-This is the numbers of folks in MACON:
```{r , echo=FALSE}
nrow(data_2[data_2$vb_vf_reg_city == "MACON", ])

```
